---
title: "dataproofr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dataproofr)
```

dataproofr is a wrapper for the excellent [dataproofer](https://github.com/dataproofer/Dataproofer) package. It automatically checks for a series of potential errors and mistakes in a dataset.

## Installation

You can install `dataproofr` with the following command: 

```{r, eval=FALSE}
remotes::install_github("nicucalcea/dataproofr")
```

dataproofr uses the [dataproofer](https://github.com/dataproofer/Dataproofer) NodeJS package under the hood, so it will need NodeJS and npm installed on your device.

After installing the library, you can run `node_available()` to check whether the necessary software is installed. If it's not, install it to use `dataproofr`.

After you've confirmed that NodeJS and npm are installed, run the following command to install [dataproofer](https://github.com/dataproofer/Dataproofer):

```{r, eval=FALSE}
dataproofer_install()
```

## Using dataproofr

The most straightforward to use the library is this:

```{r}
proof(iris)
```

There are a few optional arguments you can use. Among other things, you can specify which tests to run with `tests` or you can output the result of the tests with `out`.

```{r}
proof(iris, tests = "core", verbose = TRUE)
```
Alternatively, you can use `proof_custom()` with the arguments from the [original NodeJS library](https://github.com/dataproofer/Dataproofer):

```{r}
proof_custom(iris, options = "--core --summary")
```

You can run `proof_custom(iris, options = "--help")` for a full list of commands.
